Examining background gene list issue in clusterProfiler - RNA-seq example

### 2024-09-06 analysis/analyse_rnaseq1.Rmd
plot individual points

>>>>

## Make beeswarm chart

```{r,beeswarms}

gslibs <- unique(params2$Var2)

nsl <- lapply(gslibs,function(g) {
  orig <- subset(res1,Var2==g)$nsig_bad
  corr <- subset(res1,Var2==g)$nsig_good
  df1 <- data.frame("gsl"=g,"type"="orig","count"=orig)
  df2 <- data.frame("gsl"=g,"type"="corr","count"=corr)
  return(rbind(df1,df2))
} )

nsl <- do.call(rbind,nsl)
nsl$set <- paste(nsl$gsl,nsl$type)

unsl <- unstack(nsl[,c(3,4)])

par(mar = c(5.1, 8.1, 4.1, 2.1))
library(beeswarm)
boxplot(unsl,horizontal=TRUE,las=1,col=c("lightblue","pink"),cex=0,xlab="no. significant sets FDR<0.05")
beeswarm(unsl,horizontal=TRUE,add=TRUE,col=c("blue","red"),pch=19,cex=0.6)

par(mar = c(5.1, 4.1, 4.1, 2.1))
